\section{Motivation}

My idea behind this study originates from my own experiences growing up in Ireland, a country that has year round mild climate, where extreme weather conditions are a rarity. The winter of 2009 to early 2010, however differed from this norm, Ireland was gripped by one of its most severe cold spells in history. Ireland is not equipped to handle sub zero temperatures. My family and I faced considerable hardship when the plummeting temperatures transformed roads into treacherous ice paths, we lived on top of a steep hill which effectively isolated us. The freezing conditions led to our water pipes bursting and the central heating system failing, leaving us without water and reliant on wood logs for warmth. We walked nearly 2 miles everyday to gather basic goods to survive this spell. This period of unforeseen hardship, lasting two weeks, deeply impacted me and ignited a commitment to contributing positively to global society.

This strengthened when I moved to California in 2018, where I was captivated by the United States' breathtaking natural landscapes, from its vast national parks and diverse wildlife to its picturesque coastlines. The destruction brought by the August Complex wildfire in 2020, with its toll on life and nature, was a turning point for me. It prompted the urgency of taking action to preserve our environment.

In my professional role today, I focus on identifying and rectifying inefficiencies in manufacturing processes, I have already begun to contribute to environmental sustainability. These efforts have led to reductions in carbon emissions, and minimized raw material usage. Pursuing a graduate degree represents a continuation of this journey, driven by my belief in the power of data to effect change. With the data seemingly within reach, my goal is to deepen my understanding of how to leverage this information effectively.

This project marks a significant step towards realizing my long-term ambition of dedicating my career to the environmental sector. It is an opportunity to apply the education that I have received so far at UCLA, and to embark on a path that I hope will allow me to make a meaningful and lasting impact on our world.